---
title             : "Geospatial analysis of Cox's bazar division, Bangladesh"
shorttitle        : "Title"

author: 
  - name          : "Hafez Ahmad"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Postal address"
    email         : "ha626@msstate.edu"
    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
      - Conceptualization
      - Writing - Original Draft Preparation
      - Writing - Review & Editing
  - name          : "Ernst-August Doelle"
    affiliation   : "1,2"
    role:
      - Writing - Review & Editing

affiliation:
  - id            : "1"
    institution   : "Wilhelm-Wundt-University"
  - id            : "2"
    institution   : "Konstanz Business School"

authornote: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

  Enter author note here.

abstract: |
  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.
  
  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.
  
  One sentence clearly stating the **general problem** being addressed by  this particular study.
  
  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).
  
  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.
  
  One or two sentences to put the results into a more **general context**.
  
  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.
  
  <!-- https://tinyurl.com/ybremelq -->
  
keywords          : "keywords"
wordcount         : "X"

bibliography      : ["r-references.bib"]

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_word
---

```{r setup, include = FALSE}
library("papaja")
# loading R libraries
library (raster)       # raster data
library(rasterVis)   # raster visualization     
library(sp)          # spatial data processing          
library(rgdal)       # spatial data processing      
library(RStoolbox)   # Image analysis
library(ggplot2)     # plotting
library(gridExtra)   # plot arrangement
r_refs("r-references.bib")
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

# Introduction
we can use citation add symbol @Mukhopadhyay2018 
### git
initiate the upstream tracking of the project on the GitHub repo
git remote add origin https://github.com/hansenjohnson/website.git

pull all files from the GitHub repo (typically just readme, license, gitignore)
git pull origin master/ main

set up GitHub repo to track changes on local machine
git push -u origin master

## Landuse
## SDM
## statistical analysis
## landsaurfare temperature
## Tests
```{r}
# 
```

# Methods
We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study. <!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->

## Participants

## Material

## Procedure

## Data analysis
We used `r cite_r("r-references.bib")` for all our analyses.
```{r}
data<- data.frame(Group=rep(c('control','Test1','Test2'),each=10),value=c(rnorm(10),runif(10),rnorm(10)))
write.csv(data,'data/landsurface temperature.csv')
```
```{r}
data$Group<- as.factor(data$Group)
png('Figures_or_Maps/boxplot.png')
boxplot(value~Group,data=data)
```

## Data preprocessing 
```{r}
# loading raster and meta data 
# landsat 8-9 OLI/TIRS C2 L1
meta<- list.files('data',pattern = '.txt')
meta
```

```{r}
metafiles<- c()
for (i in 1:4){
  mfilesnames<-paste0('meta_',substr(meta[i],18,25))
  metafiles<- c(metafiles, mfilesnames)
}
```

```{r}
meta_20191203<- readMeta('W:/Home/hahmad/public/Course/Sprin 2022/WFA8990/milestone project/data/LC08_L1TP_022037_20220314_20220322_02_T1_MTL.txt')

```
```{r}
study<- readOGR('data/Oktibbeha.shp')
rasters_raw<- Sys.glob('data/*.TIF')
new_Rast<- raster(rasters_raw[1])
study<- spTransform(study, proj4string(new_Rast)) 

```

```{r}
for (i in 1:8){
  new_Rast<- raster(rasters_raw[i])
  cropped<- crop(new_Rast,extent(study))
  masked<- mask(cropped,study)
  writeRaster(masked,paste0('data',names(new_Rast)[i],'.tif'),overwrite=TRUE)
}
```

# Results

# Discussion
# Conclusion

\newpage

# References

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id="refs" custom-style="Bibliography"></div>
\endgroup
