---
title             : "Geospatial analysis of Oktibbeha County of Mississippi, USA"
shorttitle        : "Title"

author: 
  - name          : "Hafez Ahmad"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Postal address"
    email         : "ha626@msstate.edu"
    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
      - Conceptualization
      - Writing - Original Draft Preparation
      - Writing - Review & Editing
  - name          : "Ernst-August Doelle"
    affiliation   : "1,2"
    role:
      - Writing - Review & Editing

affiliation:
  - id            : "1"
    institution   : "Mississippi State University, "
  - id            : "2"
    institution   : "Konstanz Business School"

authornote: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

  Enter author note here.

abstract: |
  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.
  
  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.
  
  One sentence clearly stating the **general problem** being addressed by  this particular study.
  
  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).
  
  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.
  
  One or two sentences to put the results into a more **general context**.
  
  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.
  
  <!-- https://tinyurl.com/ybremelq -->
  
keywords          : "keywords"
wordcount         : "X"

bibliography      : ["r-references.bib"]

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_word
---

```{r setup, include = FALSE}
library("papaja")
# loading R libraries
library(tidyverse)
library (raster)       # raster data
library(rasterVis)   # raster visualization     
library(sp)          # spatial data processing          
library(rgdal)       # spatial data processing      
library(RStoolbox)   # Image analysis
library(ggplot2)     # plotting
library(gridExtra)   # plot arrangement
r_refs("r-references.bib")
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

###we can use citation add symbol [@Mukhopadhyay2018] 

### git ###initiate the upstream tracking of the project on the GitHub repo git remote add origin <https://github.com/hafez-ahmad/R-markdown-article-class.git>

###pull all files from the GitHub repo (typically just readme, license, gitignore) git pull origin master/ main

###set up GitHub repo to track changes on local machine git push -u origin master

# Introduction

we will write about vegetation, temperature and rainfall and a little bit demography

Monitoring vegetation over time is an essential component of geographical resource management applications. On-site monitoring is frequently carried out by taking detailed measurements, such as canopy level measurements. In situ measurements are time-consuming, labor-intensive, and difficult to carry out over large geographic areas. Remote sensing, on the other hand, is a very viable option for monitoring numerous vegetation characteristics using various vegetation indices such as Normalized Difference Vegetation Index, Near-Infrared / Red Ratio, Soil and atmospherically resistant vegetation index [@im2008hyperspectral].

Land cover and land use analysis are critical for determining how people and local ecosystem services interact today and in the future. It serves as the foundation for a comprehensive analysis of the research topic[@Mukhopadhyay2018].

# Methods

## Participants (First and Last name (Your email))

1.  Hafez Ahmad ([ha\@msstate.edu](mailto:ha@msstate.edu){.email})

# Material

## Study area

### we write about Oktibbeha county

Oktibbeha County is a micropolitan county in east-central Mississippi that is home to Starkville city and Mississippi State University. The county is located within Mississippi's golden triangle region. The name of the county is derived from a Native American term that means "bloody water" or "icy creek" [@gannett1902origin]. According to the 2020 United States Census, the county had 51,788 people, 17,798 households, and 9,263 families.

## Procedure

## Vegetation and Landuse \[2020_06,2021_02,2021_06,2022_02\]


$NDVI=\frac{BAND 5 - Band 4}{Band 5 + Band 4}$

Landsurface temperature was download from  
1. MOD11A2.006 Terra Land Surface Temperature and Emissivity 8-Day Global 1km 

### Data analysis

We used `r cite_r("r-references.bib")` for all our analyses.

```{r}
lst<- read_csv("data/landsurface temperature2010_22.csv")
Prci<-read_csv("data/Precipitation1998_19.csv")

```


## Data preprocessing

```{r}
# loading raster and meta data 
# landsat 8-9 OLI/TIRS C2 L1
meta<- list.files('data/raster_vector',pattern = '.txt')
meta
```

```{r}
# empty vector 
metafiles<- c()
# append all names in the metafile vector 
for (i in 1:4){
  mfilesnames<-paste0('meta_',substr(meta[i],18,25))
  metafiles<- c(metafiles, mfilesnames)
}

print(metafiles)
```

```{r}
# read meta data 
#meta_20191203<- readMeta('data/raster_vector/LC08_L1TP_022037_20220314_20220322_02_T1_MTL.txt')

```

```{r}
# read shapefile
study<-shapefile('data/raster_vector/Oktibbeha.shp')
# read all raster files
#rasters_raw<- Sys.glob('data/*.TIF')
# just one file for reprojection 
#new_Rast<- raster(rasters_raw[1])
# reproject
#study<- spTransform(study, proj4string(new_Rast)) 

```

```{r}
# Raster data processing 
#for (i in 1:8){
#  new_Rast<- raster(rasters_raw[i])
#  cropped<- crop(new_Rast,extent(study))
#  masked<- mask(cropped,study)
#  writeRaster(masked,paste0('data',names(new_Rast)[i],'.tif'),overwrite=TRUE)
#}
```

### Radiometric calibration and Atmospheric Correction

1.  Conversion DN values to spectral radiance

```{r}

```

2.  Conversion of spectral radiance to reflectance

```{r}

```

## Statistical analysis

## Land surface temperature and precipitation

## Tests

# Results
```{r}
lst_description<- lst %>% 
  summarize(Mean=round(mean(LST_Day_1km,na.rm=TRUE),2),
            Median=round(median(LST_Day_1km,na.rm=TRUE),2),
            Max=round(max(LST_Day_1km,na.rm=TRUE),2),
            Min=round(min(LST_Day_1km,na.rm=TRUE),2),
            SD=round(sd(LST_Day_1km,na.rm=TRUE),2))
lst_description[,-1] <- printnum(lst_description[,-1])

apa_table(lst_description,
          caption = 'Descriptive statistics of Land surface temperature',
          note = 'MOD11A2.006 Terra Land Surface Temperature and Emissivity 8-Day Global 1km ',
          escape = TRUE)
```


# Discussion

# Conclusion

\newpage

# References

```{=tex}
\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}
```
::: {#refs custom-style="Bibliography"}
:::

```{=tex}
\endgroup
```
